Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Signal

### 2020-08-07 Papers/02_Pulses_Envelope/PulsesEnvelope.tex
some progress in the paper

% Essential background information
We start by defining a pulse as a series of consecutive samples in a discrete wave with the same signal. More formally, let $ W[i] \in \mathbb{R} \forall i \in \mathbb{N}_0, i < n \in \mathbb{N}_0 $ be a real, discrete and finite signal indexed, without loss of generality, over a subset of the natural numbers. This definition relates closely to the concept of an array or vector in programming languages, and is used in the interest of simplicity. A pulse $ P[j], j \in \mathbb{N}_0 $ in $ W $ can then be defined as a sequence of samples indexed by $ i $ such that $ \sign(W[a-1]) \ne \sign(W[a]) = \sign(W[a+1]) = \dots = \sign(W[b-1]) = \sign(W[b]) \ne \sign(W[b+1]) \forall a \le i \le b | a,b \in \mathbb{N}_0 $; that is to say, a cluster of samples between the change of sign. For a continuous function, that would correspond to the pieces between roots, and would be equal to half the cycle of a sinusoid.

% pulse, simplified pulse, pseudo-cycle image

@@

  % \begin{figure}[h!]
  %   \centering
  %     \includegraphics[width=0.8\linewidth]{images/01ContinuousVsDiscrete.pdf}
  %   \caption{Discrete samples (black points) from a continuous wave (grey line). Note that the amplitude is also truncated}
  %   \label{fig:ContinuousVsDiscrete}
  % \end{figure}

>>>>

% Essential background information
We start by defining a pulse as a series of consecutive samples in a discrete wave with the same signal. More formally, let $ W[i] \in \mathbb{R} \forall i \in \mathbb{N}_0, i < n \in \mathbb{N}_0 $ be a real, discrete and finite signal indexed, without loss of generality, over a subset of the natural numbers. This definition relates closely to the concept of an array or vector in programming languages, and is used in the interest of simplicity. A pulse $ P[j], j \in \mathbb{N}_0 $ in $ W $ can then be defined as a sequence of samples indexed by $ i $ such that $ \sign(W[a-1]) \ne \sign(W[a]) = \sign(W[a+1]) = \dots = \sign(W[b-1]) = \sign(W[b]) \ne \sign(W[b+1]) \forall a \le i \le b | a,b \in \mathbb{N}_0 $; that is to say, a cluster of samples between the change of sign. For a continuous function, that would correspond to the pieces between roots, and would be equal to half the cycle of a sinusoid. Thus, in our analogy, two consecutive, opposed pulses have the potential do delimitate a pseudo-cycle, as illustrated in figure \ref{fig:pulses}. For that to be true, however, the pulses need to make part of the frontier, as will be defined later.

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{01Pulses.pdf}
    \caption{The grey areas encompass the simplified convex hulls of the pulses. The dashed lines mark the frontier between pseudo-cycles}
    \label{fig:pulses}
  \end{figure}

@@
